Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-07-31 volunteer-clouds-ieee-ci-si.tex
adding some references to Functional Programming Paradigm

In the work presented in this paper, JavaScript was used in the full 
stack, which has the advantage of using the same code for writing
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time when writing code and leverages %FERGU: párrafo en pasado "was used" y presente "saves"
expertise acquired in the library itself. %FERGU: tienes info de LoC usadas para la sección experimental y justificar esta frase?
%The proposed software has the advantage of full stack JavaScript
%development..
%FERGU: añadido el siguiente párrafo y referencia para justificar el uso de JS
Javascript is also compatible with the functional programming paradigm. According to 
\cite{swanresearch2015}, the benefits of using this kind of paradigm in 
metaheuristics optimization allows an improvement in communicability, 
reproducibility, interoperability, automated assembly, knowledge engineering 
and efficiency.

>>>>

In the work presented in this paper, JavaScript was used in the full 
stack, which has the advantage of using the same code for writing
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time when writing code and leverages %FERGU: párrafo en pasado "was used" y presente "saves"
expertise acquired in the library itself. %FERGU: tienes info de LoC usadas para la sección experimental y justificar esta frase?
%The proposed software has the advantage of full stack JavaScript
%development..
%FERGU: añadido el siguiente párrafo y referencia para justificar el uso de JS
Javascript is also compatible with the functional programming paradigm \cite{Cousineau1998,MacLennan1990,Thompson1996}. 
According to \cite{swanresearch2015}, the benefits of using this kind of paradigm in 
metaheuristics optimization allows an improvement in communicability, 
reproducibility, interoperability, automated assembly, knowledge engineering 
and efficiency.
